---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all(".", quiet = TRUE)
```

# splashr

<!-- badges: start -->
<!-- badges: end -->

`splashr` brings [TodePond's Splash color system](https://www.todepond.com/lab/splash/) to R.

Splash represents colors as **3-digit numbers** (`RGB`), where each digit is a
channel from `0` to `9`. There are exactly 1000 Splash colors (`000` = black,
`999` = white, `900` = red, `090` = green, `009` = blue, ...). The format is
human-readable, computer-readable, and intentionally restrictive — it helps
you stop fussing over the "perfect" color.

`splashr` converts Splash codes to hex strings you can drop straight into
plots, and supports **themes** (custom channel mappings, including TodePond's
own pastel "Cellpond" palette).

## Installation

You can install the development version of splashr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("LoonanChauvette/splashr")
```

## Getting started

```{r example}
library(splashr)

# A single Splash color
splash("900")

# Several at once
splash(c("900", "090", "009"))

# Numeric codes are zero-padded
splash(c(900, 90, 9))

# By name (theme-aware)
splash("green")
```

### Wildcards: 10-color ramps along one channel

A `_` in a code marks the channel that varies `0` to `9`, giving you a
10-step ramp that stays inside the Splash system:

```{r wildcard}
splash("9_9")   # red=9, blue=9, green varies 0..9
```

### Themes

Themes define how the 0–9 digits map to 0–255 channel values, and which
color names are available. Two themes ship with the package: `"default"`
(linear mapping) and `"cellpond"` (TodePond's personal pastel palette).

```{r themes}
splash_themes()

# Same name, different hex across themes
splash("green")
splash("green", theme = "cellpond")

# Define your own
splash_theme(
  "high-contrast",
  r = seq(0, 255, length.out = 10),
  g = seq(0, 255, length.out = 10),
  b = seq(0, 255, length.out = 10)
)
```

### Palettes for plotting

`splash_palette()` returns ready-to-use hex colors from the theme's named
backbone — drop them straight into `col =` or a scale:

```{r palette}
splash_palette(4)
splash_palette(4, theme = "cellpond")
```

```{r swatch, echo = FALSE}
splash_show(splash_palette(8))
```

### Round-tripping with `as_splash()`

`as_splash()` converts hex back to the nearest Splash code, respecting the
theme so round-trips are stable:

```{r as-splash}
as_splash("#ff0000")
as_splash(splash("407"))   # round-trip
```

## Further reading

- [The Splash color system (TodePond)](https://www.todepond.com/lab/splash/)
- `?splash`, `?splash_palette`, `?splash_theme` for full API docs
